### 2014-10-24 PrivacyProtection-2014-09-09.tex
WIP

This section outlines the potential threats for the citizen privacy in the Live+Gov system.
Recall from the security model description in section \ref{sec:GrimmModel}, that a threat is
a potential interaction of the components that harms an asset.

@@

In Figure \ref{fig:ThreatExamples} we illustrate the structure of threats at the example of ``Data Theft".
Here the attack is executed by an external person, that harms the privacy of the citizen.
He is motivated to do so by financial profit gained by selling personal information, which
is in conflict with the citizens interest in his privacy.
To get hold of the data the external exploits an insecured HTTP transfer of recorded data.

%TODO: Update Threat Table

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Threat Specification}

\textbf{Man In The Middle:}
Lorem ipsum dolor suit amet, ...

\textbf{Exploit:}
Lorem ipsum dolor suit amet, ...

\textbf{Corruption:}
Lorem ipsum dolor suit amet, ...

\textbf{Intrasparency:}
Lorem ipsum dolor suit amet, ...

\input{./figures/LG-Threats}
\input{./figures/Threat-Example-1}
\input{./figures/Threat-Example-2}
\input{./figures/ThreatTable}

@@

% Todo: use sensor privacy matrix and implicit sensor privacy matrix for threat risk evaluation

\textbf{Sensor Privacy Matrix}

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
%\input{./figures/LG-Sensor-Privacy-Matrix}
\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}

\item
\textbf{Privacy of The Person}

@@

\item \textbf{Privacy of Data and Image}

The \textbf{Privacy of Data and Image} demands, that \emph{``individual's data is not automatically available to other individuals''}.
This type of privacy is trivially threatened because here sensor data is individual data, a priori.
So every sensor violates the privacy of data and image, as data is transported into a foreign system where operators have access to it.

\item \textbf{Privacy of Location and Space}

According to Friedewald et al., the \textbf{Privacy of Location and Space} is concerned with one's \emph{``right to move about in public or semi-public space without being identified, tracked or monitored.''}.
This is the location aspect of this type. The space aspect is concerned with one's \emph{``right to solitude''}, which generally includes one's right to an inviolate home and other private spaces.
Obviously the \textbf{GPS} and \textbf{GSM} sensors violate such right about not being tracked, because they reveal the position of the mobile device and its carrier.
The \textbf{GSM} sensor gives the exact cell, the mobile device has registered with at the current moment.
The \textbf{GPS} sensor gives the current longitude and latitude, the current global position of the mobile device and its carrier, although there is some artificial inaccuracy within civil use.

>>>>

Recall from the security model description in section \ref{sec:GrimmModel}, that a threat is
a potential interaction of the components that harms an asset.

@@

\input{./figures/Threat-Example-1}

In Figure \ref{figure:ThreatExample} we illustrate the structure of threats at the example of ``Data Theft".
Here the attack is executed by an external person, that harms the privacy of the citizen.
He is motivated to do so by financial profit gained by selling personal information, which
is in conflict with the citizens interest in his privacy.
To get hold of the data the external exploits an insecured HTTP transfer of recorded data.

In this section we describe the most important threats for the citizen privacy in the Live+Gov system.

%TODO: Update Threat Table
\input{./figures/ThreatTable}

@@

@@

\textbf{Sensor Privacy Matrix}
\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}

\begin{itemize}
\item \textbf{Privacy of The Person}

@@

\item \textbf{Privacy of Data and Image}
The Privacy of Data and Image demands, that \emph{``individual's data is not automatically available to other individuals''}.
This type of privacy is trivially threatened because here sensor data is individual data, a priori.
So every sensor violates the privacy of data and image, as data is transported into a foreign system where operators have access to it.

\item \textbf{Privacy of Location and Space}
According to Friedewald et al., the Privacy of Location and Space is concerned with one's \emph{``right to move about in public or semi-public space without being identified, tracked or monitored.''}.
This is the location aspect of this type. The space aspect is concerned with one's \emph{``right to solitude''}, which generally includes one's right to an inviolate home and other private spaces.
Obviously the \textbf{GPS} and \textbf{GSM} sensors violate such right about not being tracked, because they reveal the position of the mobile device and its carrier.
The \textbf{GSM} sensor gives the exact cell, the mobile device has registered with at the current moment.
The \textbf{GPS} sensor gives the current longitude and latitude, the current global position of the mobile device and its carrier, although there is some artificial inaccuracy within civil use.
